Thermodynamic fragments in magic state theories

### 2021-02-02 magic_paper.tex
added low and high temperature limits separately

Majorization finds an important application on quantum thermodynamics in the absence of coherence.
The use of majorization in this setting provides useful intuition for our purposes.
At any given temperature $\beta$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
Roughly, the statement is that there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.

@@

Consider a qutrit system with maximally Wigner-negative magic state $\ket{\rm{S}} = \frac{1}{\sqrt{2}}(\ket{0} - \omega^2 \ket{1})$.
It can be written in density operator form as
\begin{align}
	\ketbra{\rm{S}} = \sum_{\bmx \neq (2,2)} \frac{1}{6} A_{\bmx} - \frac{1}{3} A_{(2,2)},
\end{align}
where $\bmx$ ranges in the $3$-dimensional phase space $\pd[3]$.
This is a permutation of the pure Strange state visualised in~\cref{fig:strange}.
We allow for isotropic (uniform) noise, so that the system state is a convex sum of the pure Strange state and the maximally mixed state,
\begin{equation}
	\noisys(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
\end{equation}
where we choose to restrict the noise level, $0 \leq \epsilon \leq \frac{3}{7}$, so that the Wigner distribution of the state always contains a negative component which is greater than the 8 positive components of the state.

In particular, the Wigner distribution of the state can be written as 
\begin{equation}
	\W[\bmx]{\noisys(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
\end{equation}
so we get positive components
\begin{equation}
	\wp(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
\end{equation}
at the 8 phase space points $\bmx \in \pd[3] \setminus \{(2,2)\}$ and a negative component
\begin{equation}
	- \wn(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
\end{equation}
at point $\bmx = (2,2)$.

@@

To this end, consider the general qutrit Hamiltonian
\begin{equation}
	H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2},
\end{equation}
where the energy eigenbasis coincides with the computational basis.
We have that energy eigenvalues $E_i \geq 0$, but impose no order between them.

@@

Consider a general $\epsilon$-noisy Strange state $\noisys$ in a thermal fragment $\O_{\gamma}$.
We can construct the Gibbs-rescaled distribution 
\begin{equation}
	\widetilde{\rm{W}}_{\noisys|\gamma}(\bmx) = \widetilde{\rm{W}}_1(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
\end{equation}
which naturally splits the phase space $\pd[3]$ into four regions where the ``slope'', i.e. the value of the Gibbs-rescaled distribution, is different.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
    The slope is positive in regions $X,Y,Z$, but attains a different value in each region and the slope is negative in region $1$.
    The distribution values and multiplicites (i.e. the numpber of phase space points contained in the region) can be read off as the term coefficients in~\cref{eq:g1}.
    }
    \label{fig:pd_split_thermal}
\end{figure}
In each region, we want to keep track of the corresponding values and multiplicities of Wigner distributions $\W{\noisys}, \W{\gamma}$ and Gibbs-rescaled distribution $\widetilde{\rm{W}}_1$. 
To this end, we label the four regions using variables $1,X,Y,Z$ as illustrated in~\cref{fig:pd_split_thermal}, and we write down the expressions:
\begin{align}\label{eq:g1}
	G_1(\noisys) &\coloneqq -\wn + 3\wp X + 3\wp Y + 2\wp Z \\
	\begin{split}
	G_1(\gamma) &\coloneqq (3\Z)^{-1} \big( e^{-\beta E_2} + 3e^{-\beta E_0} X \\
	&\hspace{49pt} + 3e^{-\beta E_1} Y + 2e^{-\beta E_2} Z \big) 
	\end{split}
	\\
	\begin{split}
	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -\wn e^{\beta E_2} + 3\wp e^{\beta E_0} X \\
	&\hspace{41pt} + 3\wp e^{\beta E_1} Y + 2\wp e^{\beta E_2} Z \big)
	\end{split}
\end{align}
The coefficient of each term reads as the multiplicity times the value of the desired distribution in the corresponding region.

An $n$-copy system is described over a phase space given by the $n$-times Cartesian product $\pd[3]^{\times n}$ which generates new regions of different slope.
In particular, it comprises exactly the regions $X^i Y^j Z^k$, where $i,j,k = 0,\dots,n$ and 
\begin{equation}
	\alpha \coloneqq i+j+k \leq n.
\end{equation} 
For example, region $YZ$ consists of all points expressed as the direct sum $\bmy \oplus \bmz$, where $\bmy \in Y$ and $\bmz \in Z$. \nick{abuse of notation: I use X,Y,Z as sets and as variables that represent those sets}

The $n$-copy Wigner distributions, and therefore the $n$-copy Gibbs-rescaled distribution can be written as self-convolutions,
\begin{align}
	\W{\noisys\too{n}}(\bmx) &= \W{\noisys}(\bmx)\too{n} \\
	\W{\gamma\too{n}}(\bmx) &= \W{\gamma}(\bmx)\too{n} \\
	\begin{split}
	\widetilde{\rm{W}}_{\noisys\too{n}|\gamma\too{n}}(\bmx) &= \widetilde{\rm{W}}_n(\bmx) = \frac{\W{\noisys\too{n}}(\bmx)}{\W{\gamma\too{n}}(\bmx)} \\
	&= \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} = \left( \widetilde{\rm{W}}_1(\bmx)\right) \too{n}.
	\end{split}
\end{align}
Therefore, the values and multiplicites of the $n$-copy distributions are generated directly as a multinomial expansion of the $1$-copy expressions in~\cref{eq:g1}.
\begin{align}\label{eq:gn}
	&G_n(\noisys) \coloneqq G_1(\noisys)^n = \\
	&\sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \big[(-\wn)^{n-\alpha} \wp^{\alpha} \big] X^i Y^j Z^k, \nonumber
	\\[10pt]
	&G_n(\gamma) \coloneqq G_1(\gamma)^n = \\
	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_2} \Big] X^i Y^j Z^k, \nonumber
	\\[10pt]
	&G_n(\noisys|\gamma) \coloneqq G_1(\noisys|\gamma)^n = \\
	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_2} \times \nonumber\\[-15pt]
	&\hspace{80pt} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big] X^i Y^j Z^k, \nonumber
\end{align}
where the $(i,j,k)$-th term multiplicity $m_{ijk}$ (i.e. the number of phase space points contained in region $X^i Y^j Z^k$) is given by
\begin{equation}
	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 3^i 3^j 2^k.
\end{equation}

In order to construct the Lorenz curve of a Strange state in a thermal fragment we need to sort the components of $\widetilde{W}_n$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
\begin{equation}\label{eq:max_slope}
	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_2} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}}
\end{equation}
Notice that for $0 \leq \epsilon \leq \frac{3}{7}$, we have $\wn \geq \wp$.
Assume that $n$ is even (the analysis is similar for odd $n$). 
We then need the sum $\alpha = i+j+k$ to be even, so that the expression remains positive.

Given a value for the sum $\alpha$, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_2}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_2} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{\beta n E_2} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_2)} \right)^{\alpha} \Big\}}
\end{align}
The last expression is clearly maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_2)} \leq 1$ ($>1$).
Therefore, we have
\begin{equation}
\widetilde{W}_{\rm{max}} =
	\begin{cases}
		\wn^n e^{n\beta E_2},\ &\beta \leq \frac{1}{E_{\rm{max}} - E_2}\ln{\left( 8-\frac{18}{3-\epsilon} \right)} \\
		\wp^n e^{n\beta E_{\rm{max}}},\ &\beta > \frac{1}{E_{\rm{max}} - E_2}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
	\end{cases}
\end{equation}

@@

@@

Consider the Strange state distillation process
\begin{equation}\label{eq:stdist}
	\noisys\too{n} \longrightarrow \noisys(\tt, \epsilon', n - n') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(n-\tt)},
\end{equation}
in the thermal fragment $\O_{\gamma_\beta}$.
We are now in a position to extract a distillation bound that takes the temperature $\beta$ into account in an analogous method as the one used for the unital fragment distillation bound.

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/thermal_distill.pdf}
    \caption{\textbf{Threshold dependence on temperature in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
    The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.
    }
    \label{fig:thermal_distill}
\end{figure}

>>>>

Majorization finds an important application on quantum thermodynamics in the absence of coherence.
The use of majorization in this setting provides useful intuition for our purposes.
At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
Roughly, the statement is that there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.

@@

Consider a qutrit system with maximally Wigner-negative magic state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
It can be written in density operator form as
\begin{align}
	\ketbra{\rm{S}} = -\frac{1}{3} A_{\bmo} + \sum_{\bmx \neq \bmo} \frac{1}{6} A_{\bmx},
\end{align}
where $\bmx$ ranges in the $3$-dimensional phase space $\pd[3]$.
This is the pure Strange state visualised in~\cref{fig:strange}.
We allow for isotropic (uniform) noise, so that the system state is a convex sum of the pure Strange state and the maximally mixed state,
\begin{equation}
	\noisys(\epsilon) \coloneqq (1-\epsilon)\ketbra{\rm{S}} + \epsilon \frac{1}{3}\id,
\end{equation}
where we choose to restrict the noise level, $0 \leq \epsilon \leq \frac{3}{7}$, so that the Wigner distribution of the state always contains a negative component which is greater than the remaining 8 positive components.

In particular, the Wigner distribution of the state can be written as 
\begin{equation}
	\W[\bmx]{\noisys(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
\end{equation}
so we get positive components
\begin{equation}
	\wp(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
\end{equation}
at the 8 phase space points $\bmx \in \pd[3] \setminus \{\bmo\}$ and a negative component
\begin{equation}
	- \wn(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
\end{equation}
at the origin $\bmx = \bmo$.

@@

To this end, consider the general qutrit Hamiltonian
\begin{equation}
	H = E_0 \ketbra{0} + E_1 \ketbra{1} + E_2 \ketbra{2},
\end{equation}
where the energy eigenbasis coincides with the computational basis.
We have that energy eigenvalues $E_i \geq 0$, but impose no order between them.
We denote the highest energy eigenvalue as
\begin{equation}
	E_{\rm{max}} \coloneqq \max{\{E_0, E_1, E_2\}}.
\end{equation}

@@

Consider a general $\epsilon$-noisy Strange state $\noisys$ in a thermal fragment $\O_{\gamma}$.
We can construct the Gibbs-rescaled distribution 
\begin{equation}
	\widetilde{\rm{W}}_{\noisys|\gamma}(\bmx) = \widetilde{\rm{W}}_1(\bmx) \coloneqq \frac{\W[\bmx]{\noisys}}{\W[\bmx]{\gamma}},
\end{equation}
which naturally splits the phase space $\pd[3]$ into four regions where the ``slope'', i.e. the value of the Gibbs-rescaled distribution, is different.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
    The slope is positive in regions $X,Y,Z$ and negative in region $1$.
    It attains a unique value in each region.
    The values and multiplicites can be read off as the term coefficients in~\cref{eq:g1}.
    }
    \label{fig:pd_split_thermal}
\end{figure}
In each region, we want to keep track of the number of phase space points it contains (i.e. the multiplicity) and the corresponding values of the Wigner distributions $\W{\noisys}, \W{\gamma}$ and the Gibbs-rescaled distribution $\widetilde{\rm{W}}_1$. 
To this end, we label the four regions using variables $1,X,Y,Z$ as illustrated in~\cref{fig:pd_split_thermal}, and we write down the expressions:
\begin{align}\label{eq:g1}
	G_1(\noisys) &\coloneqq -\wn + 2\wp X + 3\wp Y + 3\wp Z \\
	\begin{split}
	G_1(\gamma) &\coloneqq (3\Z)^{-1} \big( e^{-\beta E_0} + 2e^{-\beta E_0} X \\
	&\hspace{49pt} + 3e^{-\beta E_1} Y + 3e^{-\beta E_2} Z \big) 
	\end{split}
	\\
	\begin{split}
	G_1(\noisys|\gamma) &\coloneqq (3\Z) \big( -\wn e^{\beta E_0} + 2\wp e^{\beta E_0} X \\
	&\hspace{41pt} + 3\wp e^{\beta E_1} Y + 3\wp e^{\beta E_2} Z \big)
	\end{split}
\end{align}
The coefficient of each term reads as the multiplicity times the value of the desired distribution in the corresponding region.
Note that the negative Strange state Wigner component pairs with energy eigenvalue $E_0$ in region $1$.

An $n$-copy system is described over a phase space given by the $n$-times Cartesian product $\pd[3]^{\times n}$ which generates new regions of different slope.
In particular, it comprises exactly the regions $X^i Y^j Z^k$, where $i,j,k = 0,\dots,n$ and 
\begin{equation}
	\alpha \coloneqq i+j+k \leq n.
\end{equation}
For example, region $YZ$ consists of all points expressed as the direct sum $\bmy \oplus \bmz$ or $\bmz \oplus \bmy$, where $\bmy \in Y$ and $\bmz \in Z$.
Note that there is no difference between e.g. regions $YZ$ and $ZY$, since multiplication of slopes is commutative. 
\nick{abuse of notation: I use X,Y,Z as sets and as variables that represent those sets}

The $n$-copy Wigner distributions $\W{\noisys\too{n}}, \W{\gamma\too{n}}$, and consequently the $n$-copy Gibbs-rescaled distribution $\widetilde{\rm{W}}_n = \widetilde{\rm{W}}_{\noisys\too{n}|\gamma\too{n}}$ can be written as self-convolutions,
\begin{align}
	\W{\noisys\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n) &= \W{\noisys}(\bmx_1)\dots\W{\noisys}(\bmx_n) \nonumber\\
	&= \W{\noisys}(\bmx)\too{n} \\[10pt]
	\W{\gamma\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n) &= \W{\gamma}(\bmx_1)\dots\W{\gamma}(\bmx_n) \nonumber\\
	&= \W{\gamma}(\bmx)\too{n} \\[10pt]
	\widetilde{\rm{W}}_n(\bmx_1 \oplus \dots \oplus \bmx_n) &= \frac{\W{\noisys\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n)}{\W{\gamma\too{n}}(\bmx_1 \oplus \dots \oplus \bmx_n)} \\
	= \frac{\W{\noisys}(\bmx_1)\dots\W{\noisys}(\bmx_n)}{\W{\gamma}(\bmx_1)\dots\W{\gamma}(\bmx_n)} &= \left( \frac{\W{\noisys}(\bmx)}{\W{\gamma}(\bmx)} \right)\too{n} \nonumber\\
	&= \left( \widetilde{\rm{W}}_1(\bmx)\right) \too{n}. \nonumber
\end{align}
Therefore, the values and multiplicites of the $n$-copy distributions are generated directly as a multinomial expansion of the $1$-copy expressions in~\cref{eq:g1}.
\begin{align}\label{eq:gn}
	&G_n(\noisys) \coloneqq G_1(\noisys)^n = \\
	&\sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \big[(-\wn)^{n-\alpha} \wp^{\alpha} \big] X^i Y^j Z^k, \nonumber
	\\[10pt]
	&G_n(\gamma) \coloneqq G_1(\gamma)^n = \\
	&(3\Z)^{-n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ e^{-\beta ( i E_0 + j E_1 + k E_2 )} e^{-\beta (n-\alpha)E_0} \Big] X^i Y^j Z^k, \nonumber
	\\[10pt]
	&G_n(\noisys|\gamma) \coloneqq G_1(\noisys|\gamma)^n = \\
	&(3\Z)^{n}\hspace{-10pt} \sum\limits_{\substack{i,j,k = 0,\dots,n \\ \alpha \leq n}}\hspace{-10pt} m_{ijk} \Big[ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} \times \nonumber\\[-15pt]
	&\hspace{80pt} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big] X^i Y^j Z^k, \nonumber
\end{align}
where the $(i,j,k)$-th term multiplicity $m_{ijk}$ (i.e. the number of phase space points contained in region $X^i Y^j Z^k$) is given by
\begin{equation}
	m_{ijk} \coloneqq \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
\end{equation}

In order to construct the Lorenz curve of a Strange state in a thermal fragment we need to sort the components of $\widetilde{W}_n$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
\begin{equation}\label{eq:max_slope}
	\widetilde{W}_{\rm{max}} \coloneqq \max\limits_{i,j,k}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}}
\end{equation}
Notice that for $0 \leq \epsilon \leq \frac{3}{7}$, we have $\wn \geq \wp$.
Assume that $n$ is even (the analysis is similar for odd $n$). 
We then need the sum $\alpha = i+j+k$ to be even, so that the expression remains positive.

Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
The last expression is clearly maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than or equal to $1$ (greater than $1$).
We want to rewrite the expression as a noise level $\epsilon$ constraint with respect to temperature $\beta^{-1}$, where the noise threshold is
\begin{equation}
	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
\end{equation}
The noise threshold $\epsilon_{\rm{th}}$ is an increasing function of temperature $\beta^{-1}$.
We have
\begin{equation}
\widetilde{W}_{\rm{max}} =
	\begin{cases}
		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}}, 	\\
		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.
	\end{cases}
\end{equation}

For low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, we get $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
This scenario includes the unital fragment, defined at the limit $\beta \rightarrow 0$, because for $\beta = 0$, we have $\epsilon_{\rm{th}} = 3/7$, so $\epsilon \leq \epsilon_{\rm{th}}$ always holds.

In the low noise level scenario, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$,
\begin{equation}
	(x_0, L_0) = ((3\Z)^{-n}, \wn^n)
\end{equation}
and the necessary distillation constraint defined at the location $x_\star = x_0$ of the initial state's first elbow is
\begin{equation}\label{eq:first_elbow_constraint}
	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
\end{equation}

The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_temp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3\Z_\beta)^{\tt-n} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
\end{equation}
The process in~\cref{eq:stdist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} \geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta \Big]}} = \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta F_\beta}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta F_\beta},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
The free energy of thermal state $\gamma_\beta$ is denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] - \beta^{-1} \tr[\gamma_\beta \log{\gamma_\beta}].
\end{equation}

Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$.
In fact, for any
\begin{equation}
	\beta \geq \beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2,
\end{equation}
we always have $\epsilon_{\rm{th}} \leq 0$, so $\epsilon \geq \epsilon_{\rm{th}}$.
Note that if $E_{\rm{max}} = E_0$, the bound is infinite, simply meaning that $\epsilon = \epsilon_{\rm{th}}$ at the limit $\beta = \infty$.
In the low temperature scenario, we get $\widetilde{W}_{\rm{max}} = \wn^p e^{n\beta E_{\rm{max}}}$ occuring in a region labelled by 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(n,0,0), &E_{\rm{max}} = E_0, \\
	(0,n,0), &E_{\rm{max}} = E_1, \\
	(0,0,n), &E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
The bound expression does not depend on which energy is the highest so, without loss of generality, assume that $E_{\rm{max}} = E_0$.
Then, the multiplicity is $m_{n00} = 2^n$ and the first elbow coordinates can be read off the $X^nY^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$,
\begin{equation}
	(x_0, L_0) = \left( \left(\frac{2}{3}\frac{e^{-\beta E_0}}{\Z_\beta}\right)^n, (2u)^n \right)
\end{equation}
and the distillation constraint is defined at the location $x_\star = x_0$ of the initial state's first elbow as in~\cref{eq:first_elbow_constraint}.

The first elbow of the target state is located at $x'_0 = (2e^{-\beta E_0} / (2\Z_\beta))^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_lowtemp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = 2^n \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{6} - \frac{1}{18}\epsilon' \right)^{\tt}.
\end{equation}
Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the distillation process in~\cref{eq:stdist} is possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} - \beta F_\beta + \beta E_{\rm{max}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} - \beta F_\beta + \beta E_{\rm{max}}},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon$.

@@

For $\beta = 0$, $\epsilon_{\rm{th}} = 3/7$, so $\epsilon \leq \epsilon_{\rm{th}}$ always.
In this case, $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.

For 	
\begin{equation}
	\beta \geq \beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2,
\end{equation}
$\epsilon_{\rm{th}} \leq 0$, so $\epsilon \geq \epsilon_{\rm{th}}$ always.

For $0 < \beta < \beta_{\rm{th}}$, the order between energy eigenvalues matters.
\begin{itemize}
\item If $E_{\rm{max}} = E_0$, only the first case is valid, since the noise constraint becomes $\epsilon \leq 3/7$.
In this case, $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
\item If $E_{\rm{max}} = E_1$, then for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wp^n e^{n\beta E_1}$ occuring in the region labelled by $(i,j,k) = (0,n,0)$.
\item If $E_{\rm{max}} = E_2$, then for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$ and for high noise levels $\epsilon > \epsilon_{\rm{th}}$, $\widetilde{W}_{\rm{max}}  = \wp^n e^{n\beta E_2}$ occuring in the region labelled by $(i,j,k) = (0,0,n)$.
\end{itemize}

@@

Consider the Strange state distillation process
\begin{equation}\label{eq:stdist}
	\noisys\too{n} \longrightarrow \noisys(\tt, \epsilon', n - n') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(n-\tt)},
\end{equation}
in the thermal fragment $\O_{\gamma_\beta}$.
We are now in a position to extract a distillation bound that takes the temperature $\beta^{-1}$ into account in an analogous method as the one used for the unital fragment distillation bound.

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/thermal_distill.pdf}
    \caption{\textbf{Threshold dependence on temperature in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon' = 0.05$.
    The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}^{-1}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.
    }
    \label{fig:thermal_distill}
\end{figure}
